---
title: "Assignment 1"
---

# Assignment 1

My first assignment has two parts.

## (b)

```{r}
library(dslabs)
data(polls_us_election_2016)
head(polls_us_election_2016)
```

```{r}
my_first <- "Asiye"
my_birth_year <- 2003
print(paste("My first name is", my_first))
print(paste("My birth year is", my_birth_year))
k <- as.integer((nchar(my_first) + my_birth_year) %% 15 + 8)
print(paste("The k value is:", k))
```

```{r}
k <- as.integer((nchar(my_first) + my_birth_year) %% 15 + 8)
if (k %% 2 == 0) {
  head(polls_us_election_2016, k)
} else {
  tail(polls_us_election_2016, k)
}
```

```{r}
print(paste("The total number of NA values is:", sum(is.na(polls_us_election_2016))))

column_Na <- colSums(is.na(polls_us_election_2016))

sorted_Na <- sort(column_Na, decreasing = TRUE)

head(sorted_Na, 8)

```
I used AI to help me build this loop. The prompt I used was: I have a dataset in R and I want to fill the NA values based on the column type. How can I set up a loop that puts a specific number if the column is numeric, and a specific string if it's text or a factor? I also want to keep the original data frame intact.

```{r}
polls_modified <- polls_us_election_2016

for(i in 1:ncol(polls_modified)) {
  
  if(is.numeric(polls_modified[[i]])) {
    polls_modified[[i]] <- ifelse(is.na(polls_modified[[i]]), 
                                  my_birth_year + k, 
                                  polls_modified[[i]])
    
  } else if(is.character(polls_modified[[i]]) | is.factor(polls_modified[[i]])) {
    polls_modified[[i]] <- ifelse(is.na(polls_modified[[i]]), paste0(my_first, "_", k), polls_modified[[i]])
  }
}
if (k %% 2 == 0) {
  head(polls_modified, k)
} else {
  tail(polls_modified, k)
}
```

```{r}
total_na_remaining <- sum(is.na(polls_modified))
print(paste("The total number of NA values remaining is:", total_na_remaining))
```

Since there is no NA value remaining this function will gonna be FALSE

```{r}
anyNA(polls_modified)
```

## (b)
